Application of Huynh 2020 Interim Analysis methods to assessed stocks from the US South Atlantic

### 2022-03-16 RunMSE/SEFSC/MSEPlots.Rmd
updated rds files

---
title: "Application of Huynh 2020 Interim Analysis methods to assessed stocks from the US South Atlantic"
author: "Nikolai Klibansky"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies:
      longtable: null
      xcolor: null
urlcolor: blue
---

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.height=7,fig.width=6)

@@

```{r user}
OMNames_user <- c("OM_BlackSeaBass","OM_VermilionSnapper","OM_RedPorgy")#,
                   #"OM_Tilefish","OM_Cobia","OM_SnowyGrouper",
                   #"OM_capelin", "OM_POP", "OM_vs"
                   #)
scenNames_user <-  c("base",#"hs","hd",
                     "dep","lf",
                     "epiM"
                     )
scenNames_key <- c("base"="Base","hs"="Hyper-stable","hd"="Hyper-deplete",
                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M")
MPNamesSub_user <- c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10")
MPNamesSub_user_legtext <- c("Fixed TAC (10)","Annual assessment","Averaged Index (10)","Buffered Index (10)")

@@

```{r plot_LH function}
plot_LH <- function(OM,...){
maxage <- OM@maxage
agebins <- 0:maxage
lenbins <- vb_len(Linf=OM@Linf[1],K=OM@K[1],t0=OM@t0[1],a=agebins)
Plenbins <- lenbins/max(lenbins)
Mat_age <- OM@cpars$Mat_age[1,,1] # Maturity at age
V <- OM@cpars$V[1,,1] # Vulnerability (selectivity) at age

@@

```{r plot_MSE_ts_Huynh function}

plot_MSE_ts_Huynh <- function(
myvarName,
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean_noNA,
scenNames,
OMNames,
MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10"),
MPNamesSub_legtext=MPNamesSub,
legtext_o = c(2,3,4,1), # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,

mar=c(1,1,1,1),
cols = setNames(c("red","black","deepskyblue2","deepskyblue2"),MPNamesSub),
ltys = setNames(c(1,1,1,2),MPNamesSub),
lwds = setNames(c(3,3,3,3),MPNamesSub),
types = setNames(c("l","l","l","l"),MPNamesSub),
xlabel = "Management year",
xlim = NULL,
ylim = NULL,
assessmentYears = seq(10,40,by=10),
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.6),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){
xlim_user <- xlim
ylim_user <- ylim
x.at_user <- x.at
y.at_user <- y.at

@@

nrow <- length(rowLabs)
ncol <- length(colLabs)
npanel <- nrow*ncol

par(mfcol=c(nrow,ncol),mgp=c(1,0.2,0),mar=mar,oma=c(6,4,3,3),tck=-0.01,xpd=FALSE,xaxs="i",yaxs="i")

@@

if(is.null(ylim_user)){
  ylim <- range(myvarsubStat,na.rm=TRUE)
}
if(is.null(xlim_user)){
  xlim <- range(as.numeric(rownames(myvarsubStat)),na.rm=TRUE)
}

matplot(as.numeric(rownames(myvarsubStat)),myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)

grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty="1111",lwd=2)
if(!is.null(hline)){
abline(h=hline)
}

@@

>>>>

---
title: "Application of Huynh 2020 Interim Analysis methods to assessed stocks from the US South Atlantic"
author: "Nikolai Klibansky"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies:
      longtable: null
      xcolor: null
      pdflscape: null
urlcolor: blue
---

```{r setup, include=FALSE, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10)

@@

```{r user}
# Should individual PDFs be produced (or just plot in Rmd output)
plot_pdf <- TRUE

OMNames_user <- c("OM_BlackSeaBass",
                  "OM_VermilionSnapper",
                  "OM_RedPorgy",
                   #"OM_Tilefish","OM_Cobia",
                  "OM_SnowyGrouper"#,
                  #"OM_GagGrouper")#,
                   #"OM_capelin", "OM_POP", "OM_vs"
                   )
OMNames_huynh <- c("OM_CapelinHuynh", "OM_PacificOceanPerchHuynh", "OM_VermilionSnapperHuynh")

scenNames_user1 <-  c("base","dep","lf","epiM","ubias","tachi","rc")
scenNames_user2 <-  c("base","nolag","minerr","minrecdev","perfobs","ucvhi","ucvlo","vtiv"
                        )

# All scenarios
scenNames_user <- unique(c(scenNames_user1,scenNames_user2))

# Alternative realities
# These scenarios are considered equally plausible, for the purposes of
# averaging results together. Most other scenarios could be considered sensitivities.
scenNames_user_alt <- c("base","dep","lf","epiM","ubias","tachi","rc")

scenNames_key <- c("base"="Base",
                   "nolag"="No data lag",
                   "hs"="Hyper-stable","hd"="Hyper-deplete",
                   "dep"="Depleted","lf"="Lightly fished","epiM"="Episodic M",
                   "rc"="Regime\nchange", "ubias"="Index\nbiased","ucvhi"="Index\nHigh CV",
                   "ucvlo"="Index\nLow CV",
                   "perfobs"="Perfect observation",
                   "minerr"="Minimal error",
                   "minrecdev"="Minimal rec devs",
                   "tachi"="TAC 1.25MSY",
                   "vtiv"="V time invariant"
                   )

MPNamesAll <-         c(#"AvC",
                        "CC1",
                        #"DCAC","DBSRA","SPMSY",
                        "SCA_1","SCA_5","SCA_10",
                        "iMP_avg_5","iMP_avg_10",
                        "iMP_buffer_5","iMP_buffer_10",
                        "pMP_5","pMP_10"
                        )

MPNamesAll_key <- c("AvC"="average catch",
                    "CC1"="average catch (last 5 yr)",
                    "DCAC"= "depletion corrected average catch",
                    "DBSRA" = "depletion based stock reduction analysis",
                    "SPMSY" = "surplus production model",
                    "SCA_1" = "SCA 1 yr",
                    "SCA_5" = "SCA 5 yr",
                    "SCA_10"= "SCA 10 yr",
                    "iMP_avg_5" = "avg. index (5 yr)",
                    "iMP_avg_10" = "avg. index (10 yr)",
                    "iMP_buffer_5" = "buffer index (5 yr)",
                    "iMP_buffer_10" = "buffer index (10 yr)",
                    "pMP_5" = "projection (5 yr)",
                    "pMP_10" = "projection (10 yr)"
                        )
MPNamesAll_legtext <- MPNamesAll

MPNamesSub_user <- c("SCA_10","SCA_5","SCA_1","iMP_avg_10"#,"iMP_buffer_10"
                     )
MPNamesSub_user_legtext <- c("Fixed TAC (10)","Fixed TAC (5)","Annual assessment","Averaged Index (10)"#,"Buffered Index (10)"
                             )

@@

## Built in performance metrics (PMs)

* `P10`	  Probability B > 0.1 BMSY
* `P50`	  Probability B > 0.5 BMSY
* `P100`  Probability B > BMSY
* `PNOF`  Probability F < FMSY
* `LTY`	  Probability Long-Term Yield > 0.5 Relative Yield
* `STY`	  Probability Short-Term Yield > 0.5 Relative Yield
* `AAVY`	Probability AAVY < 0.2 (Average Annual Variability in Yield)
* `AAVE`	Probability AAVE < 0.2 (Average Annual Variability in Effort)
* `Yield`	Average Yield (relative to Reference Yield)

- can easily vary reference values and years
- PMs compute probabilities across years for each simulation and return mean values across simulations (but we could recompute them however we want from the raw MSE objects)

```{r functions}
# color function like rainbow() but without yellow (or indigo)
ROGBP <- colorRampPalette(c("red","orange","green","blue","purple"))
# Makes an ROGBP function with an alpha channel
ROGBP_alpha <- function(alpha){
  x <- colorRampPalette(c(
    rgb(1,0,0,alpha), # red
    rgb(1,0.5,0.25,alpha), # orange
    rgb(0,1,0,alpha), # green 
    rgb(0,0,1,alpha), # blue
    rgb(0.5,0,0.5,alpha)), # purple
    alpha=TRUE)
  return(x)
}

# Turn hexadecimal color opaque
makeOpaque <-      function(hexcolor){gsub(".{2}$","FF",hexcolor)}

P75 <- function(...,Ref=0.75){P50(...,Ref=Ref)}

AAVY10 <- function(MSEobj = NULL, Ref = 0.1, Yrs = NULL){AAVY(MSEobj = MSEobj, Ref = Ref, Yrs = Yrs)}

```{r plot_LH function}
plot_LH <- function(OM,...){
maxage <- OM@maxage
agebins <- 0:maxage
lenbins <- vb_len(Linf=OM@Linf[1],K=OM@K[1],t0=OM@t0[1],a=agebins)
Plenbins <- lenbins/max(lenbins)
styr_proj <- OM@nyears+1
Mat_age <- apply(OM@cpars$Mat_age[,,styr_proj],2,mean) # Maturity at age
V <- apply(OM@cpars$V[,,styr_proj],2,mean) # Vulnerability (selectivity) at age

@@

```{r plot_MSE_ts function}
# Time series plots

plot_MSE_ts <- function(
myvarName="SSB",
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = mean,
scenNames,
OMNames,
MPNamesSub = NULL,
MPNamesSub_legtext=MPNamesSub,
MPNamesRef = NULL, # Name of reference MP
FUNRef = function(myvarsubStat,MPNamesRef){ # Function for comparing MPs with reference MP
  (myvarsubStat-myvarsubStat[,MPNamesRef])/myvarsubStat[,MPNamesRef]},
legtext_o = NULL, # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,
sims = NULL, # which simulation runs should be used to generate the plot when plot_type="sims"?
plot_type="huynh", # "huynh" plots time series by MP like in the Huynh et al paper
                   # "boot" plots times series of bootstrapped data  with bamExtras::plot_boot_vec
                   # "phase" plots phase plots of F/Fmsy versus SSB/SSBmsy
                   # "tradeoff" plots tradeoff plots by MP
                   # "addind" plot additional indices from AddInd
                   # "sims" plot time series for individual sim runs
proyear_phase=NULL,
PMx = Yield, # Performance metric function x (x-axis) for tradeoff plots)
PMy = P75, # Performance metric function y (y-axis) for tradeoff plots)
mar=c(1,1,1,1),
oma=c(6,4,3,3),
mgp=c(1.5,0.2,0),
cols = setNames(ROGBP_alpha(0.5)(length(MPNamesSub)),MPNamesSub),
ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
lwds = setNames(rep(3,length(MPNamesSub)),MPNamesSub),
types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
xlabel = "Management year",
main_line = 1, # Line for main column labels
xlim = NULL,
ylim = NULL,
assessmentYears=NULL,
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
legend_panel=NULL,
legend_cex= 1,
legend_x="bottomleft",
legend_inset=c(0,-0.5),
label_axes="all", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){
if(is.null(legtext_o)){
  legtext_o <- seq_along(MPNamesSub)
}

xlim_user <- xlim
ylim_user <- ylim
x.at_user <- x.at
y.at_user <- y.at

@@

dim1 <- length(rowLabs)
dim2 <- length(colLabs)

if(plot_type=="addind"){
  mfcol <- c(dim2,dim1)}else{
  mfcol <- c(dim1,dim2)
}

par(mfcol=mfcol,mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="r",yaxs="r")

### LOOP THROUGH MSE OBJECTS
for(outName_i in MSEoutNames){
topPanels <- (length(scenNames)*(seq_along(OMNames)-1)+1)
bottomPanels <- length(scenNames)*seq_along(OMNames)
leftPanels <- seq_along(scenNames)
rightPanels <- tail(seq_along(MSEoutNames),length(scenNames))

i <- which(MSEoutNames==outName_i)
out_i <- get(outName_i)
MPNames <- out_i@MPs

if(is.null(sims)){
  sims <- 1:out_i@nsim
}
if(!is.expression(myvarName)){
  myvar <- slot(out_i,myvarName)  
}else{
  myvar <- eval(myvarName) 
}

nyears_i <- out_i@nyears
proyears_i <- out_i@proyears
LHyear_i <- out_i@Hist@Data@LHYear # Last historic year
histYears <- sort(LHyear_i - ((1:nyears_i)-1))
projYears_i <- LHyear_i+1:proyears_i

MPNamesSubix <- match(MPNamesSub,MPNames)

if(plot_type=="huynh"){
if(!is.null(dim(myvar))){
myvarsub <- myvar[,match(MPNamesSub,MPNames),]
myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
}else{
myvarsubStat <- matrix(rep(myvar,length(MPNamesSub)),ncol=length(MPNamesSub))  
}
dimnames(myvarsubStat) <- list(1:nrow(myvarsubStat),MPNamesSub)

if(!is.null(MPNamesRef)){
myvarsubStat <- FUNRef(myvarsubStat,MPNamesRef)
}

if(is.null(ylim_user)){
  ylim <- range(myvarsubStat,na.rm=TRUE)
}
if(is.null(xlim_user)){
  xlim <- range(projYears_i,na.rm=TRUE)
}

matplot(projYears_i#as.numeric(rownames(myvarsubStat))
        ,myvarsubStat,
        col=cols,lty=ltys,lwd=lwds,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)

grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty="1111",lwd=2)
}
    if(plot_type=="sims"){
      cols <-  ROGBP(length(sims))
      ltys <-  1:length(MPNamesSub)
      pchs <-  NA
      lwds <-  3
      types <- "l"

      myvarsub <- myvar[sims,match(MPNamesSub,MPNames),,drop=FALSE]
      dimnames(myvarsub) <- list(sims,MPNamesSub,1:proyears_i)

      if(!is.null(MPNamesRef)){
        myvarsub <- FUNRef(myvarsub,MPNamesRef)
      }

      if(is.null(ylim_user)){
        ylim <- range(myvarsub,na.rm=TRUE)
      }
      if(is.null(xlim_user)){
        xlim <- range(projYears_i,na.rm=TRUE)
      }

      for(MP_j in MPNamesSub){
      j <- match(MP_j,MPNamesSub)
      myvarsub_j <- myvarsub[,j,]
      lty <- ltys[j]
      if(j==1){
      matplot(projYears_i,
              t(myvarsub_j), 
              col=cols,lty=lty,lwd=lwds,type=types,
              xaxt=xaxt_i,yaxt=yaxt_i,
              xlim=xlim,ylim=ylim,xlab="",ylab="")
      #title(main=colLabsAll[i],line=1)

      grid(nx=NA,ny=NULL)
      abline(v=assessmentYears,lty=2,lwd=1)
      }else{
        matpoints(t(myvarsub_j), 
                col=cols,lty=lty,lwd=lwds,type=types
                )        
      }
    }
    }

if(plot_type=="addind"){
  PPDYears_i <- local({
    a <- c(histYears,projYears_i)
    a[-length(a)]
  })
if(is.null(assessmentYears)){
assessmentYears <- apply(do.call(cbind,lapply(out_i@PPD[[MPNamesSub]]@Misc,FUN=function(x){x1 <- x$diagnostic; unlist(lapply(x1,FUN=function(xx){xx$Year}))})),1,median)
}

if(!is.null(dim(myvar))){
myvarsub <- myvar
#myvarsubStat <- apply(myvarsub,2,function(x){apply(x,2,FUN)})
}else{
  warning("is.null(dim(myvar) == TRUE. No option currently available for this situation.")
}
dimnames(myvarsub) <- list("sim"=1:dim(myvarsub)[1],"AddInd"=1:dim(myvarsub)[2],"Year"=PPDYears_i)
if(is.null(ylim_user)){
  ylim <- range(myvarsub,na.rm=TRUE)
}
if(is.null(xlim_user)){
  xlim <- range(PPDYears_i,na.rm=TRUE)
}
# n_AddInd <- ncol(myvarsubStat)
# cols <-  ROGBP_alpha(0.5)(n_AddInd)
# matplot(PPDYears_i,myvarsubStat,
#         col=cols,lty=ltys,lwd=lwds,type=types,
#         xaxt=xaxt_i,yaxt=yaxt_i,
#         xlim=xlim,ylim=ylim,xlab="",ylab="")
#title(main=colLabsAll[i],line=1)
n_AddInd <- dim(myvarsub)[2]
col_AddInd <- ROGBP(n_AddInd)
for(j in 1:n_AddInd){

plot_boot_vec(myvarsub[,j,],
              col_lines = col_AddInd[j],
              add=ifelse(j!=1,TRUE,FALSE),
              xlim=xlim,ylim=ylim)

}
grid(nx=NA,ny=NULL)
abline(v=assessmentYears,lty=2,lwd=1)
}

if(plot_type=="boot"){
  if(is.null(ylim_user)){
  ylim <- range(myvar,na.rm=TRUE)
}
  bamExtras::plot_boot_vec(myvar,ylim=ylim)
  abline(v=out_i@nyears,lwd=2,lty=2) # Plot vertical line at end of historical period
}

if(plot_type=="phase"){
ltys <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
# pchs <-  setNames(rep(1,length(MPNamesSub)),MPNamesSub)
lwds <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
types <- setNames(rep("p",length(MPNamesSub)),MPNamesSub)  
xlabel <- "F/Fmsy"  
ylabel <- "SSB/SSBmsy"

if(is.null(proyear_phase)){
  proyear_phase <- out_i@proyears
}
Bstatus <- out_i@SB_SBMSY[,MPNamesSubix,proyear_phase]
Fstatus <- out_i@F_FMSY[,MPNamesSubix,proyear_phase]

matplot(Fstatus,Bstatus,
        col=cols,lty=ltys,lwd=lwds,pch=pchs,type=types,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlab="",ylab="",xlim=xlim,ylim=ylim
        )
points(apply(Fstatus,2,median),
       apply(Bstatus,2,median),pch=21,cex=3,lwd=2,col="black",bg=makeOpaque(cols))

  abline(v=1,lty=3)
  abline(h=1,lty=3)

}

if(plot_type=="tradeoff"){
  out_i <- get(outName_i)

PMx_out <- PMx(out_i)
PMy_out <- PMy(out_i)

plot(PMx_out@Mean[MPNamesSubix],PMy_out@Mean[MPNamesSubix],pch=16,col=cols,
     xaxt=xaxt_i,yaxt=yaxt_i,
     xlab="",ylab="",
     xlim=xlim,ylim=ylim
     )

# legend("top",legend=MPs,col=MPcols,pch=16,bty="n")

ltys <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
lwds <-  setNames(rep(0,length(MPNamesSub)),MPNamesSub)
types <- setNames(rep("p",length(MPNamesSub)),MPNamesSub)  
xlabel <- PMx_out@Caption 
ylabel <- PMy_out@Caption

}

if(!is.null(hline)){
abline(h=hline)
}

if(i%in%topPanels){
col.ct <- which(topPanels==i)
mtext(colLabsAll[i],side=3,line=main_line,outer=FALSE,font=2)
}

if(i%in%rightPanels){
row.ct <- which(rightPanels==i)
rowcenter <-par("usr")[3]+diff(par("usr")[3:4])/2
text(x=par("usr")[2]+diff(par("usr")[1:2])*0.1
     ,y=rowcenter,rowLabsAll[i],
     srt=-90,xpd=NA,font=2)
}

if(label_axes=="all"){
  x.at.i <- x.at
  axis(side=1,at=x.at.i)
  y.at.i <- y.at
  axis(side=2,at=y.at.i)
}
if(label_axes=="leftbottom"){
  if(i%in%bottomPanels){
    x.at.i <- x.at
    if(i>bottomPanels[1]){x.at.i <- x.at[-1]}
    axis(side=1,at=x.at.i,outer=TRUE)
  }
  if(i%in%leftPanels){
    y.at.i <- y.at
    if(i>leftPanels[1]){y.at.i <- y.at[1:(length(y.at)-1)]}
    axis(side=2,at=y.at.i,outer=TRUE)
  }
}

if(i==legend_panel&plot_type%in%c("huynh","phase","tradeoff")){
   legend(legend_x,
          inset=legend_inset,
       horiz=TRUE,bty="n",
       legend=MPNamesSub_legtext[legtext_o],
       col=makeOpaque(cols)[legtext_o],lty=ltys[legtext_o],lwd=lwds[legtext_o],pch=pchs[legtext_o],
       cex=legend_cex,
       xpd=NA,
       x.intersp=0.5
       )

mtext(ylabel,side=2,line=par("mgp")[1],outer=TRUE)
mtext(xlabel,side=1,line= par("mgp")[1],outer=TRUE)

```{r plot_MSE_dw function}
# Dot and whisker plots

plot_MSE_dw <- function(
myvarName,
myvarDenomExpr = NULL,
ylabel = myvarName,
FUN = cv,  # MSEtool::cv
scenNames,
OMNames,
MPNamesSub = c("SCA_10","SCA_1","iMP_avg_10","iMP_buffer_10"),
MPNamesSub_legtext=MPNamesSub,
legtext_o = c(3,2,1,4), # order for plotting legend text
MSEoutNames = paste0(rep(gsub("OM","MSE",OMNames),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames))
                     ),
colLabs = str_replace_all(gsub("OM_","",OMNames),"(?<=[a-z])(?=[A-Z])"," "),
rowLabs = scenNames,

mar=c(0,0,0,0),
oma=c(10,4,3,3),
mgp=c(1,0.3,0),
cols = setNames(ROGBP(length(MPNamesSub)),MPNamesSub),
ltys = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
lwds = setNames(rep(1,length(MPNamesSub)),MPNamesSub),
pchs = setNames(rep(16,length(MPNamesSub)),MPNamesSub),
types = setNames(rep("l",length(MPNamesSub)),MPNamesSub),
textlabpos = rep("lo",length(MSEoutNames)),#c(rep("lo",6),rep("up",7),"lo",rep("up",4)),
xlabel = "Management procedure",
xlabel_line=9,
xlim = NULL,
ylim = c(0,0.6),
x.at = NULL,
y.at = NULL,
# leg.x=NULL,
# leg.y =NULL,
# legend_panel=NULL,
# legend_cex= 1,
# legend_x="bottomleft",
# legend_inset=c(0,-0.6),
label_axes="leftbottom", # "all" labels all panels, "leftbottom" labels y axes on the left and x axes on the bottom panels
hline=1 # values to pass into abline(h=hline)
){

xlim_user <- xlim
ylim_user <- ylim
x.at_user <- x.at
y.at_user <- y.at

nrow <- length(rowLabs)
ncol <- length(colLabs)

par(mfcol=c(nrow,ncol),mgp=mgp,mar=mar,oma=oma,tck=-0.01,xpd=FALSE,xaxs="i",
    yaxs="r",lend="butt")

@@

if(is.null(xlim_user)){
  xlim <- c(0,length(MPNamesSub)+1)
}

################################

Statmed <- apply(myvarsubStat,2,median)
Statmedtext <- round(Statmed,2)
StatQ1 <- apply(myvarsubStat,2,quantile,probs=0.25,na.rm=TRUE)
StatQ3 <- apply(myvarsubStat,2,quantile,probs=0.75,na.rm=TRUE)

xaxt_i <- ifelse(i%in%bottomPanels,"n","n")
yaxt_i <- ifelse(i%in%leftPanels,"n","n")
x <- seq_along(MPNamesSub)
plot(x,Statmed,
        col=cols,pch=pchs,type="n",bg="white",
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")
arrows(x0=x,y0=StatQ1,y1=StatQ3,
       col=cols,lty=ltys,lwd=lwds,length=0
       )
points(x,Statmed,
        col=cols,pch=pchs,type="p",bg="white",cex=1.2,
        xaxt=xaxt_i,yaxt=yaxt_i,
        xlim=xlim,ylim=ylim,xlab="",ylab="")

if(textlabpos[i]=="lo"){text(x=x,y=rep(par("usr")[3]),labels=Statmedtext,srt=90,adj=c(-0.1,0.5),font=2)}
if(textlabpos[i]=="up"){text(x=x,y=rep(par("usr")[4]),labels=Statmedtext,srt=90,adj=c(1.2,0.5),font=2)}

################################

@@

```{r plot_MSE_sims function}
plot_MSE_sims <- function(MSE, sims=NULL, MPs=NULL, proyears_ix=NULL,
              varNames=NULL, rec_age=0,
              type="proj", # period to plot: "proj", or "histproj"
              title_main = NULL,
              vline=NULL,vline_lty=3,
              ...){
MSEName <- deparse(substitute(MSE))
if(is.null(varNames)){
  varNames <- list("proj"=    c("Catch","FM","F_FMSY","recruit","SSB","SB_SBMSY"),
                   "histproj"=c("Catch","FM","F_FMSY","recruit","SSB","SB_SBMSY"))[[type]]
}

nyears <- MSE@nyears
proyears <- MSE@proyears
LHyear <- MSE@Hist@Data@LHYear # Last historic year
histYears <- sort(LHyear - ((1:nyears)-1))
projYears <- LHyear+1:proyears

if(is.null(sims)){sims <- 1:3}  
if(is.null(MPs)){MPs <- MSE@MPs[1]}
if(is.null(proyears_ix))    {proyears_ix <- 1:proyears}

MPn <- match(MPs,MSE@MPs)

nr <- ceiling(sqrt(length(varNames)))
nc <- ceiling(length(varNames)/nr)
par(mfcol=c(nr,nc),mar=c(2,3,1,1),oma=c(0,0,2,0),mgp=c(1,0.2,0),tck=-0.01)

for(varName_i in varNames){
  for(MPn_j in  MPn){
    MPn_j_ix <- match(MPn_j,MPn)
    if(type=="proj"){
      years_plot <- projYears
      if(varName_i=="recruit"){
        N <- Reduce("+",apply(MSE@Misc$extended$N,5,FUN=function(x){x},simplify = FALSE))
        var_i <- N[,rec_age+1,,]
        years_ix <-   tail(1:dim(var_i)[3],MSE@proyears)
        # drop MP dimension but not sims
        varSub_i <- var_i[sims,MPn_j,years_ix,drop=FALSE]
        varSub_i <- matrix(varSub_i,nrow=dim(varSub_i)[1],ncol=dim(varSub_i)[3]) 
      }else{
        var_i <- slot(MSE,varName_i)
        varSub_i <- var_i[sims,MPn_j,proyears_ix,drop=FALSE]
        varSub_i <- matrix(varSub_i,nrow=dim(varSub_i)[1],ncol=dim(varSub_i)[3]) 
      }
    }

    if(type=="histproj"){
      years_plot <- c(histYears, projYears)
      if(varName_i=="recruit"){
        N <- Reduce("+",apply(MSE@Misc$extended$N,5,FUN=function(x){x},simplify = FALSE))
        var_i <- N[,rec_age+1,,]
      }
      if(varName_i%in%c("F","FM")){
        FM <- apply(MSE@Misc$extended[["FM"]],c(1,3,4),max) # Max F over ages and areas
        var_i <- FM
      }
      if(varName_i=="F_FMSY"){
        FM <- apply(MSE@Misc$extended[["FM"]],c(1,3,4),max) # Max F over ages and areas
        FMSY <- MSE@RefPoint$FMSY
        var_i <- FM/FMSY
      }
      if(varName_i=="SB_SBMSY"){
        SSB <- apply(MSE@Misc$extended[["SSB"]],c(1,3,4),sum) # Sum SSB over ages and areas
        SSBMSY <- MSE@RefPoint$SSBMSY
        var_i <- SSB/SSBMSY
      }
      if(!varName_i%in%c("F","FM","recruit","F_FMSY","SB_SBMSY")){
        var_i <- Reduce("+",apply(MSE@Misc$extended[[varName_i]],5,FUN=function(x){x},simplify = FALSE))
        var_i <- Reduce("+",apply(var_i,2,FUN=function(x){x},simplify = FALSE))
      }
      #varSub_i <- var_i[sims,MPn_j,] # Drops dimension to be matrix
        varSub_i <- var_i[sims,MPn_j,,drop=FALSE]
        varSub_i <- matrix(varSub_i,nrow=dim(varSub_i)[1],ncol=dim(varSub_i)[3]) 
    }
    if(match(MPn_j,MPn)==1){
      matplot(years_plot,t(varSub_i),type="l",
              col=ROGBP(length(sims)),xlab="",ylab=varName_i, lty=MPn_j_ix,...)
    }else{
      matpoints(years_plot,t(varSub_i),type="l",
                col=ROGBP(length(sims)),lty=MPn_j_ix,...)
    }    
  }
  if(match(varName_i,varNames)==1){
    legend("topright",legend=MPs,lty=1:length(MPs),bty="n")
  }
  if(is.null(vline)){vline <- LHyear}
  abline(v=vline,lty=vline_lty)
}
if(is.null(title_main)){
  title_main <- paste(MSEName,MPs,sep=": ")
}
title(main=title_main,outer = TRUE)
}

```{r function PMsummary}
# compute and plot summary statistics for Performance metrics
PMsummary <- function(PMName,OMNames=OMNames_user,scenNames,MPs=NULL,
                      slot_to_plot="Prob", # Can be either "Prob" or "Stat"
                      main_line=-1.5,
                      hline=1,hline_lty=1,
                      par_args=list(mfrow=c(length(OMNames),1), 
                                    mar=c(0,2,0,1), oma=c(6,2,1,0),
                                    mgp=c(0.8,0.2,0), tck=-0.01),
                      ...){
PM <- get(PMName)
dots <- list(...)
if(!"ylab"%in%names(dots)){
  dots$ylab <- PMName
}

out_list <- list()

do.call(par,par_args)

for (OMNames_i in OMNames){
Names_i <- gsub("^OM_","",OMNames_i)
MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                     "_",
                     rep(scenNames,length(OMNames_i))
                     )
    out_list_i <- list()
    for(MSEoutNames_ij in MSEoutNames_i){
      scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
      MSEout_ij <- get(MSEoutNames_ij)
      PMout_ij <- PM(MSEout_ij)
        MPs_ij <- PMout_ij@MPs
        out_ij <- slot(PMout_ij,slot_to_plot)
      if(!is.null(MPs)){
        out_ij <- out_ij[,match(MPs,MPs_ij)]
        MPs_ij <- MPs
      }
      dimnames(out_ij) <- list("sim"=seq(1:dim(out_ij)[1]), "MPs"=MPs_ij)
      out_ij <- cbind("scen"=scenNames_j,as.data.frame(out_ij))
      out_list_i[[MSEoutNames_ij]] <- out_ij

    }
    # Combine scenario outputs into large data frame with scen column indicating scenario
      out_df_i <- do.call(rbind,out_list_i)
      out_list[[paste0("out_df_",Names_i,"_",PMName)]] <- out_df_i
    # Plot stuff
      dots$xaxt <- ifelse(match(OMNames_i,rev(OMNames))==1,"s","n")

      do.call(boxplot,c(list(out_df_i[,-1],main=""),dots))
      mtext(Names_i,side=3,line=main_line,outer=FALSE,font=2)
      abline(h=hline,lty=hline_lty)
    }

invisible(out_list)
}
```

```{r function MSEsummary}
# compute and plot summary statistics for Performance metrics
MSEsummary <- function(MSEslotName,OMNames=OMNames_user,scenNames,MPs=NULL,
                       main_line=-1.5,
                       hline=1,hline_lty=1,
                      par_args=list(mfrow=c(length(OMNames),1),
                                    mar=c(3,2,1,1), oma=c(1,2,0,0),
                                    mgp=c(0.8,0.2,0), tck=-0.01),
                      ...){
dots <- list(...)
if(!"ylab"%in%names(dots)){
  dots$ylab <- MSEslotName
}
out_list <- list()

do.call(par,par_args)

for (OMNames_i in OMNames){
  Names_i <- gsub("^OM_","",OMNames_i)
  MSEoutNames_i = paste0(rep(gsub("OM","MSE",OMNames_i),each=length(scenNames)),
                         "_",
                         rep(scenNames,length(OMNames_i))
  )
  slot_list_i <- list()
  for(MSEoutNames_ij in MSEoutNames_i){
    scenNames_j <- str_extract(MSEoutNames_ij,"[a-z]+$")
    MSEout_ij <- get(MSEoutNames_ij)
    if(!is.expression(MSEslotName)){
      slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
    }else{
      slot_k <- eval(MSEslotName) %>% apply(2,as.numeric)
    }
    slot_k <- slot(MSEout_ij,MSEslotName) %>% apply(2,as.numeric)
    MPs_ij <- MSEout_ij@MPs
    if(!is.null(MPs)){
      slot_k <- slot_k[,match(MPs,MPs_ij)]
      MPs_ij <- MPs
    }
    dimnames(slot_k) <- list(NULL, "MPs"=MPs_ij)
    slot_k <- cbind("scen"=scenNames_j,as.data.frame(slot_k))
    slot_list_i[[MSEoutNames_ij]] <- slot_k
